\documentclass[a4paper]{article}
\usepackage[scale=0.833333]{geometry}
\usepackage{shortvrb}
\MakeShortVerb{\|}
\newcommand{\PkgVersion}{1.0}
\newcommand{\Pkg}[1]{\textsf{#1}}
\newcommand{\Meta}[1]{$\langle$\mbox{}#1\mbox{}$\rangle$}
\newcommand{\Note}{\par\noindent \textbf{NB:}\quad}
\newcommand{\Means}{~:\quad}
%-----------------------------------------------------------
\begin{document}
\title{\Pkg{bxbase} Package (v\PkgVersion)\\
(User-level Commands)}
\author{Takayuki YATO (aka.~``ZR'')}
\date{2013/04/29}
\maketitle

%===========================================================
\section{Package Loading}

Use |\usepackage| as usual, with no options.
\begin{quote}\small\begin{verbatim}
\usepackage{bxbase}
\end{verbatim}\end{quote}

\Note This package itself, as support library, does not
depent on particular engines or DVI-wares.
However, the commands described below may have
such dependency.

%===========================================================
\section{Usage}

\begin{itemize}
\item |\recordpapersize|\Means
Outputs at the top of DVI a ``papersize special''
in the follwoing form:
\begin{quote}\small\begin{verbatim}
papersize=<width>,<height>
\end{verbatim}\end{quote}
there width and height mean the current value of
|\paperwidth| and |\paperheight|.
\Note Papersize specials are supported by some DVIwares,
such as dvips, dvipdfmx, dviout, etc.,
but not by pdf\TeX.
 
\item |\dvipdfmxmapfile{|\Meta{modifier}\Meta{file name}|}|\Means
Declares a font map file for dvipdfmx in a document.
There \Meta{modifier} is either empty (replace), |+|~(append),
or |-|~(delete).
Only valid for dvipdfmx.
\Note It outputs at the top of DVI a special of the following form:
\begin{quote}\small\begin{verbatim}
pdf:mapfile <modifier><file name>
\end{verbatim}\end{quote}


\item |\dvipdfmxmapline{|\Meta{modifier}\Meta{map line}|}|\Means
Declares a font map line for dvipdfmx in a document.
The usage of \Meta{modifier} is the same as
in the previous item.
Only valid for dvipdfmx.
\Note It outputs at the top of DVI a special of the following form:
\begin{quote}\small\begin{verbatim}
pdf:mapline <modifier><map line>
\end{verbatim}\end{quote}

\end{itemize}

%===========================================================
\end{document}
